Lock-free Skiplist-based Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-03-10 paper/paper.tex
\nocite{*} is not needed anymore
Further work on evaluation, L&S sections
Benching note
Hardware description TODO
Minor further work

@@

\citeauthor{shavit2000skiplist} were the first to propose the use of SkipLists
for priority queues \cite{linden2013skiplist}. Their initial implementation
\cite{shavit2000skiplist} builds on \citeauthor{pugh1998concurrent}'s concurrent
SkipList idea \cite{pugh1998concurrent} which uses one lock per node per level.
\citeauthor{herlihy2012art} \cite{herlihy2012art} later succeeded in making this
priority queue lock-free (but not linearizable) and provide a Java implementation
which we will examine further in the following.

% TODO

@@

% TODO: Figures, interpretation. Mention that Noble requires pointers -> new/delete.

>>>>

% TODO: Maybe integrate into description - otherwise remove. Do we need further detail?

\begin{lstlisting}
struct slist_t {
  size_t max_level;
  node_t head[max_level];
};

struct node_t {
  key_t key;
  value_t value;
  size_t level;
  node_t next[level];
};

/* All operations are expected O(log n) time. */
void slist_insert(slist_t *l, key_t k, value_t v);
bool slist_delete(slist_t *l, key_t k, value_t &v);
\end{lstlisting}

@@

\citeauthor{shavit2000skiplist} were the first to propose the use of SkipLists
for priority queues \cite{linden2013skiplist}. Their initial implementation
\cite{shavit2000skiplist} builds on \citeauthor{pugh1998concurrent}'s concurrent
SkipList \cite{pugh1998concurrent} which uses one lock per node per level.

A crucial observation is that nodes nodes which are only partially connected
do not affect correctness of the data structure. As soon as the first level (i.e. \lstinline|node.level[0]|)
has been successfully connected, a node is considered to be in the SkipList.
Therefore, both insertions and deletions can proceed in steps - insertions proceed bottom-up while
deletions proceed top-down, holding locks only for the current level.

\citeauthor{herlihy2012art} \cite{herlihy2012art} later described a variant of this idea 
that is lock-free and quiescently consistent (but not linearizable).

@@

% TODO: Figures, interpretation. Mention that Noble requires pointers -> new/delete.
% Better hardware description - see SprayList section 4.
% Note: Strong degradation of noble PQ with growing initial size.
